\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}

\geometry{margin=1in}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\pagestyle{fancy}
\fancyhf{}
\rhead{Athletix - SRS}
\lhead{Software Requirements Specification}
\rfoot{Page \thepage}

\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{2cm}
    
    {\Huge\bfseries Athletix\par}
    \vspace{0.5cm}
    {\Large A Fitness Intelligence Technology\par}
    \vspace{2cm}
    
    {\Large\bfseries Software Requirements Specification (SRS)\par}
    \vspace{3cm}
    
    {\large
    \textbf{Team Members:}\\[0.5cm]
    Khawaja Mohammad Abdullah Ishaq \quad 22P-9375\\
    Azhan Shoaib \quad 22P-9054\\
    Subhan Tariq \quad 22P-9067\\
    \vspace{1cm}
    
    \textbf{Supervised By:}\\[0.5cm]
    Dr. Muhammad Amin\\
    }
    
    \vfill
    
    {\large \today\par}
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}

\subsection{Purpose}
The purpose of this document is to define the software requirements for \textbf{Athletix – Fitness Intelligence Technology}, a cross-platform AI-powered mobile application that serves as a Virtual Fitness Trainer. It provides personalized workouts, culturally adaptable diet plans, and real-time form analysis using Computer Vision, Machine Learning, Reinforcement Learning, and Natural Language Processing.

The document serves as a reference for the development team, stakeholders, and evaluators to ensure a clear understanding of project objectives, functional requirements, and system behavior.

\subsection{Scope}
Athletix aims to bridge the gap between traditional personal training and AI-driven digital health solutions by providing:

\begin{itemize}[leftmargin=*]
    \item Real-time posture correction and exercise analysis via HRNet-based pose estimation.
    \item Adaptive workout planning and diet generation based on user goals, body attributes, and preferences.
    \item Reinforcement learning-enabled personalization that evolves as the user progresses.
    \item Conversational AI trainer (RAG + fine-tuned LLM) for guidance, exercise substitutions, and recovery tips.
    \item Culturally and medically adaptable diet planning (e.g., halal, diabetic, vegan options).
    \item Progress tracking and gamified visualization for engagement.
\end{itemize}

\subsection{Definitions, Acronyms, and Abbreviations}
\begin{table}[h!]
\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{10cm}}
\toprule
\textbf{Term} & \textbf{Description} \\
\midrule
AI & Artificial Intelligence \\
ML & Machine Learning \\
CV & Computer Vision \\
RL & Reinforcement Learning \\
LLM & Large Language Model \\
RAG & Retrieval-Augmented Generation \\
FAISS & Facebook AI Similarity Search (Vector Database) \\
HRNet & High-Resolution Network (Pose Estimation) \\
TFLite & TensorFlow Lite (for mobile inference) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{References}
\begin{enumerate}[leftmargin=*]
    \item Lewis et al. (2020), \textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}, NeurIPS.
    \item Ahmad et al. (2022), \textit{Mobile Apps for Human Nutrition: A Review}.
    \item Riccio et al. (2021), \textit{Real-Time Fitness Exercise Classification and Counting from Video Frames}.
    \item United States Department of Agriculture (2023), \textit{FoodData Central}.
    \item World Health Organization (2024), \textit{Physical Activity Guidelines}.
    \item Expert Consultation: Dr. Znair Azam – Certified Fitness Trainer \& Nutritionist.
\end{enumerate}

\newpage
\section{Overall Description}

\subsection{Product Perspective}
Athletix is an intelligent fitness assistant that operates as a standalone mobile app. It integrates:

\begin{itemize}[leftmargin=*]
    \item \textbf{Frontend:} React Native (cross-platform)
    \item \textbf{Backend:} FastAPI with PostgreSQL \& FAISS vector DB
    \item \textbf{AI Modules:} TensorFlow Lite, PyTorch, MediaPipe/HRNet, and Hugging Face Transformers
\end{itemize}

The system interacts with:
\begin{itemize}[leftmargin=*]
    \item Camera for real-time pose detection
    \item Nutrition databases (USDA API)
    \item Local data storage and cloud backup for user profiles and progress
\end{itemize}

\subsection{Product Functions}
\begin{enumerate}[leftmargin=*]
    \item \textbf{User Authentication:} Secure signup/login with profile setup.
    
    \item \textbf{User Profiling:} Collect body attributes (height, weight, age, gender, fitness goal, medical/cultural constraints).
    
    \item \textbf{Form Analysis Module:}
    \begin{itemize}
        \item Detect exercise form using HRNet keypoints.
        \item Compare with biomechanics-based correct pose templates.
        \item Provide instant feedback and correction suggestions.
    \end{itemize}
    
    \item \textbf{Workout Planner:}
    \begin{itemize}
        \item Generate customized workout plans using ML models based on user profile and goal.
        \item Reinforcement Learning adapts plans weekly based on progress.
    \end{itemize}
    
    \item \textbf{Diet Planner:}
    \begin{itemize}
        \item Generate diet plans via constraint-based optimization and contextual bandits.
        \item Ensure macro balance and cultural/medical compliance.
    \end{itemize}
    
    \item \textbf{Virtual AI Trainer (RAG + LLM):}
    \begin{itemize}
        \item Provide natural language answers to user queries.
        \item Offer modifications, recovery tips, and machine usage guidance.
    \end{itemize}
    
    \item \textbf{Progress Tracker:}
    \begin{itemize}
        \item Visual graphs showing progress in body metrics, calorie intake, and workout adherence.
        \item Gamified badges for motivation.
    \end{itemize}
    
    \item \textbf{Offline Mode:}
    \begin{itemize}
        \item On-device inference using TensorFlow Lite for real-time analysis without cloud dependency.
    \end{itemize}
\end{enumerate}

\subsection{User Characteristics}
\begin{table}[h!]
\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{9cm}}
\toprule
\textbf{User Type} & \textbf{Description} \\
\midrule
Beginner & Users new to fitness who need step-by-step guidance and visual form feedback. \\
Intermediate & Users with experience seeking adaptive plans and diet tracking. \\
Medical/Cultural Users & Users requiring restrictions (e.g., halal, diabetic). \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Constraints}
\begin{itemize}[leftmargin=*]
    \item Real-time processing limited by mobile hardware.
    \item Requires camera permissions for pose detection.
    \item Limited connectivity may affect RAG model responses.
    \item Dataset collection requires diversity to avoid bias.
\end{itemize}

\subsection{Assumptions and Dependencies}
\begin{itemize}[leftmargin=*]
    \item Users provide accurate input for body attributes.
    \item External APIs (USDA, WHO) remain accessible.
    \item TensorFlow Lite supports optimized HRNet on targeted devices.
\end{itemize}

\newpage
\section{Specific Requirements}

\subsection{Functional Requirements}
\begin{table}[h!]
\centering
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Description} \\
\midrule
FR-1 & User Authentication & Login and registration via email or Google account. \\
FR-2 & User Profiling & Collect personal and fitness data for plan generation. \\
FR-3 & Pose Detection & Capture live video, extract body keypoints, analyze form using HRNet. \\
FR-4 & Workout Generation & ML-based personalized workout plan based on goal. \\
FR-5 & Diet Recommendation & Constraint-based optimizer generates daily diet plan. \\
FR-6 & Virtual Trainer & RAG + fine-tuned LLM handles all fitness-related Q\&A. \\
FR-7 & Reinforcement Learning Engine & Adapt workout/diet plans weekly based on feedback and progress. \\
FR-8 & Progress Tracking & Visual analytics dashboard for calories, weight, workout adherence. \\
FR-9 & Data Storage & PostgreSQL for structured data; FAISS for vector retrieval. \\
FR-10 & Offline Functionality & On-device inference for pose and progress tracking. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Non-Functional Requirements}
\begin{table}[h!]
\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{10cm}}
\toprule
\textbf{Category} & \textbf{Description} \\
\midrule
Performance & App should provide feedback within 500ms after each pose frame. \\
Security & Encrypt all user data; JWT authentication for API access. \\
Scalability & Support multiple concurrent users via asynchronous FastAPI. \\
Portability & Run on both Android and iOS via React Native. \\
Usability & Simple, intuitive UI with real-time visual feedback. \\
Reliability & Maintain >95\% uptime during usage sessions. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Software Interfaces}
\begin{itemize}[leftmargin=*]
    \item \textbf{Frontend $\leftrightarrow$ Backend:} REST APIs (FastAPI)
    \item \textbf{Backend $\leftrightarrow$ AI Models:} TensorFlow Lite and PyTorch
    \item \textbf{Backend $\leftrightarrow$ Database:} PostgreSQL (user data), FAISS (LLM retrieval)
    \item \textbf{External APIs:} USDA, WHO, Nutritionix
\end{itemize}

\subsection{Hardware Interfaces}
\begin{itemize}[leftmargin=*]
    \item Mobile camera (for form analysis)
    \item Microphone (for future voice-based trainer queries)
    \item Local storage (for temporary data caching)
\end{itemize}

\subsection{Communication Interfaces}
\begin{itemize}[leftmargin=*]
    \item HTTPS for all API communication
    \item WebSocket for real-time updates
\end{itemize}

\section{System Design Constraints}
\begin{itemize}[leftmargin=*]
    \item Model quantization and pruning required for HRNet on mobile.
    \item RAG responses must be filtered for medical accuracy.
    \item Offline caching for rural or low-connectivity users.
\end{itemize}

\section{Future Enhancements}
\begin{itemize}[leftmargin=*]
    \item Integration of wearable sensor data (heart rate, steps).
    \item Voice-based interaction for hands-free training.
    \item Community and leaderboard features.
    \item Multi-language support.
\end{itemize}

\section{Appendices}

\subsection{Tools \& Technologies}
\begin{table}[h!]
\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{9cm}}
\toprule
\textbf{Component} & \textbf{Technology} \\
\midrule
Frontend & React Native \\
Backend & FastAPI \\
Database & PostgreSQL + FAISS \\
AI Models & HRNet, MediaPipe, Hugging Face Transformers \\
ML Frameworks & TensorFlow Lite, PyTorch \\
Optimization & Scipy, Pyomo \\
Version Control & GitHub \\
\bottomrule
\end{tabular}
\end{table}

\end{document}